### 2024-03-20 sections/4gluing_alt.tex
Pushing previous changes.

>>>>

\begin{remark}
    The simple case when the collar-gluing is a disjoint union, and the manifolds are smooth can also be found as \cite[ex.5.4.5.4]{lurie_ha}.
\end{remark}

\subsection{An Outside View of Factorization Algebras}

After the results of the previous section we remark on a general view that we can take for the $\infty$-categories of (locally constant) factorization algebras. Namely, we notice factorization algebras can be cast as a functor
%
\begin{equation}
    \falg_{-}(\catC), \lcfa_{-}(\catC): \mfld[r] \xrightarrow{\ \ \ \ } \cat^{\mathsf{op}},
\end{equation}
%
where the action on morphisms is given by restriction, which is what gives rise to the $^{\mathsf{op}}$.

\begin{proposition}
    Factorization algebras can be formulated as functors
    %
    \begin{equation}
        \falg_{-}(\catC), \lcfa_{-}(\catC): \mfld \xrightarrow{\ \ \ \ } \cat^{\mathsf{op}}.
    \end{equation}
\end{proposition}

\begin{proof}
    The proof will go along the same lines for both, so we will focus on factorization algebras, and shorten notation to $\mathscr{F} := \falg (\catC): \mfld[r] \xrightarrow{} \cat^{\mathsf{op}}$. Beyond the obvious assignment on objects, to define the functor we need to provide a map of spaces
    %
    \begin{equation}
        \mathsf{Hom}_{\mfld}(M, N) \xrightarrow{\ \ \eta \ \ } \mathsf{Fun}(\mathscr{F}(N), \mathscr{F}(M))^{\simeq}.
    \end{equation}
    %
    This data can be provided in the form of a map of simplicial sets, whose components are
    %
    \begin{equation}
        \mathsf{Emb}_{\Delta^p}(M \times \Delta^p, N \times \Delta^p) \xrightarrow{\ \ \eta_p \ \ } \mathsf{Fun}(\mathscr{F}(N), \mathscr{F}(M))^{\simeq}_p,
    \end{equation}
    %
    where the morphism space notation was introduced in \Cref{def:mfld_infty_cat}. Any map from a space will factor through the maximal $\infty$-groupoid of the codomain, so that we can drop the $^{\simeq}$ requirement on the target. Unraveling the definition of a functor category at the same time means that we need to provide maps
    %
    \begin{equation}
        \mathsf{Emb}_{\Delta^p}(M \times \Delta^p, N \times \Delta^p) \xrightarrow{\ \ \eta_p \ \ } \mathsf{Hom}_{\mathsf{sSet}}(\mathscr{F}(N) \times \Delta^p, \mathscr{F}(M)).
    \end{equation}
    %
    But indeed,
    %
    \begin{align}
        \mathsf{Emb}_{\Delta^p}(M \times \Delta^p, N \times \Delta^p) \xhookrightarrow{\ \ \ \ \ \ \ }& \mathsf{Emb}(M \times \Delta^p, N \times \Delta^p) \\
        \xrightarrow{\mathrm{restrict}}& \mathsf{Hom_{sSet}} (\mathscr{F}(N \times \Delta^p), F(M \times \Delta^p)) \\
        \xrightarrow{\ \pi_{1*} \circ -}& \mathsf{Hom_{sSet}} (F(N \times \Delta^p) , F(M)) \\
        \xrightarrow{\ - \circ \alpha^p \ }& \mathsf{Hom_{sSet}} (F(N) \times \Delta^p , F(M))
    \end{align}

    WORK IN PROGRESS.
\end{proof}

In the case of disjoint union, \Cref{thm:gluing_lcfas} and \Cref{cor:gluing_falgs} then provide the equivalences that are needed to make this into a symmetric monoidal functor, where the symmetric monoidal product on $\cat^{\mathsf{op}}$ is given by \emph{coproduct}. With that understanding the same two results, \Cref{thm:gluing_lcfas} and \Cref{cor:gluing_falgs}, can be understood as saying that the functors $\falg(\catC)$ and $\lcfa(\catC)$ satisfy $\otimes$-excision as outlined in \Cref{sec:excision_homology}.% We can even work a bit more to show:
%
%\begin{proposition}
%    The functors $\falg(\catC)$ and $\lcfa(\catC)$ respect sequential colimits.
%\end{proposition}
%
%\begin{proof}
%    The proof will go along the same lines for both, so we will focus on factorization algebras, and shorten notation to $\mathscr{F} := \falg (\catC): \mfld[r] \xrightarrow{} \cat^{\mathsf{op}}$. We will also use the convention that we work in $\cat$ instead of its opposite. In these terms, the statement we need to prove is that the canonical functor
%    %
%    \begin{equation}
%        \mathscr{F}(M) \xrightarrow[\alpha]{\ \ \simeq \ \ } \mathsf{lim} (\mathscr{F}(M_0) \xleftarrow{} \mathscr{F}(M_1) \xleftarrow{} \dots)
%    \end{equation}
%    %
%    is an equivalence of $\infty$-categories, where $M := \cup_{i \geq 0} M_i$. All functors used to make the diagram are restriction functors. 
%
%    An object of the limit is a collection $(A_0, A_1, \dots)$ of factorization algebras on $M_0, M_1, \dots$, respectively, together with equivalences $\eta_i: A_{i+1}|_{M_i} \simeq A_i$ for $i \geq 0$.
%\end{proof}

### 2024-03-20 sections/5classification.tex
Pushing previous changes.

In fact, technically, the only cases we need to consider are when $d=0$ --- the case of pointed Euclidean spaces, which are alternatively denoted $\mathbb{R}^n_*$. This is because of the isomorphism
%
\begin{equation}
    \mathbb{R}^{d \subset n} \cong \mathbb{R}^{n-d}_* \times \mathbb{R}^d,
\end{equation}
%
together with \Cref{prop:exp_of_products_lc}, which describes locally constant factorization algebras on product spaces. Since $\mathbb{R}^n_*$ is a basic the collar-gluing property \Cref{cor:gluing_lcfas} can't help us to analyze the situation. We are left with two cases: $n=1$ and $n > 1$. To get a better grasp on the data, we first explore the more complicated case of $n > 1$ by examining the $\infty$-operad $\disk(\mathsf{D}_{0 \subset n}^*)$, when $n > 1$.

@@

\begin{remark}
    The study of locally constant factorization algebras on $\mathbb{R}^n_*$ was also undertaken in \cite[sec.6.3]{ginot2015}. \Cref{thm:classif_Rn*}, as it appears above, is slightly different in its statement compared to the corresponding \cite[cor.8]{ginot2015}. We believe that this is due to the fact that using the homotopy pullback is not what the proof provided in the reference actually does. The remaining discrepancy is then explained by our \Cref{cor:gluing_lcfas}, which glues locally constant factorization algebras.
\end{remark}

@@

Locally, near the defect, the locally constant factorization algebra is, of course, going to look like a locally constant factorization algebra over $\mathbb{R}^{d \subset n}$. However, it is possible that the global topology introduces some twisting of this local understanding. Due to \Cref{cor:gluing_lcfas} and the properties of stratified manifolds, in any particular case, it's possible to find some list of collar-gluings that reduce the problem down to the local case, but this doesn't tell us anything about the general structure. Despite this, there is a particular collar-gluing that is the obvious first step if we're looking at a general manifold $M_\Sigma$. We will now describe this.

@@

\Cref{cor:gluing_lcfas} allows us to use the collar-gluing from above to write the equivalence of $\infty$-categories
%
\begin{equation}
    \lcfa_{M_\Sigma} (\catC) \simeq \lcfa_{M \setminus \Sigma} (\catC) \bigtimes_{\lcfa_{\mathsf{L}_\Sigma \times \mathbb{R}} (\catC)} \lcfa_{\cone(\pi)} (\catC),
\end{equation}
%
as a first step in the classification of locally constant factorization algebras on $M_{\Sigma}$. Since we have focused on stratified manifolds with the particular form $M_{\Sigma}$, the locally constant factorization algebras $\lcfa_{M \setminus \Sigma}$ in this decomposition already live on a smooth manifold, rather than on a stratified one. Similarly, this is the case for the locally constant factorization algebras $\lcfa_{\mathsf{L}_\Sigma \times \mathbb{R}}$. The more prescient question is about the classification of locally constant factorization algebras on the one remaining stratified space $\cone(\pi)$.

>>>>

In fact, technically, the only cases we need to consider are when $d=0$ --- the case of pointed Euclidean spaces, which are alternatively denoted $\mathbb{R}^n_*$. This is because of the isomorphism
%
\begin{equation}
    \mathbb{R}^{d \subset n} \cong \mathbb{R}^{n-d}_* \times \mathbb{R}^d,
\end{equation}
%
together with \Cref{prop:exp_of_products_lc}, which describes locally constant factorization algebras on product spaces. Since $\mathbb{R}^n_*$ is a basic the collar-gluing property \Cref{thm:gluing_lcfas} can't help us to analyze the situation. We are left with two cases: $n=1$ and $n > 1$. To get a better grasp on the data, we first explore the more complicated case of $n > 1$ by examining the $\infty$-operad $\disk(\mathsf{D}_{0 \subset n}^*)$, when $n > 1$.

@@

\begin{remark}
    The study of locally constant factorization algebras on $\mathbb{R}^n_*$ was also undertaken in \cite[sec.6.3]{ginot2015}. \Cref{thm:classif_Rn*}, as it appears above, is slightly different in its statement compared to the corresponding \cite[cor.8]{ginot2015}. We believe that this is due to the fact that using the homotopy pullback is not what the proof provided in the reference actually does. The remaining discrepancy is then explained by our \Cref{thm:gluing_lcfas}, which glues locally constant factorization algebras.
\end{remark}

@@

Locally, near the defect, the locally constant factorization algebra is, of course, going to look like a locally constant factorization algebra over $\mathbb{R}^{d \subset n}$. However, it is possible that the global topology introduces some twisting of this local understanding. Due to \Cref{thm:gluing_lcfas} and the properties of stratified manifolds, in any particular case, it's possible to find some list of collar-gluings that reduce the problem down to the local case, but this doesn't tell us anything about the general structure. Despite this, there is a particular collar-gluing that is the obvious first step if we're looking at a general manifold $M_\Sigma$. We will now describe this.

@@

\Cref{thm:gluing_lcfas} allows us to use the collar-gluing from above to write the equivalence of $\infty$-categories
%
\begin{equation}
    \lcfa_{M_\Sigma} (\catC) \simeq \lcfa_{M \setminus \Sigma} (\catC) \bigtimes_{\lcfa_{\mathsf{L}_\Sigma \times \mathbb{R}} (\catC)} \lcfa_{\cone(\pi)} (\catC),
\end{equation}
%
as a first step in the classification of locally constant factorization algebras on $M_{\Sigma}$. Since we have focused on stratified manifolds with the particular form $M_{\Sigma}$, the locally constant factorization algebras $\lcfa_{M \setminus \Sigma}$ in this decomposition already live on a smooth manifold, rather than on a stratified one. Similarly, this is the case for the locally constant factorization algebras $\lcfa_{\mathsf{L}_\Sigma \times \mathbb{R}}$. The more prescient question is about the classification of locally constant factorization algebras on the one remaining stratified space $\cone(\pi)$.
